---
title: "Lab 4"
author: "Sarah Roffo"
date: "10/10/2017"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---
##Question 1: The number of points scored by each team in a tournament is normally distributed, with mean = 32 and standard deviation = 7. What is the probability of:

###Question 1a: What is the probability of a team scoring 20 points or fewer? Plot the density function and shade the area: 

```{r}
pnorm(20, mean = 32, sd = 7)
curve(dnorm(x, mean = 32, sd = 7), from = 11, to = 53)
cord.x <- c(11, seq(11, 20, by = 0.01), 20)
cord.y <- c(0, dnorm(seq(11, 20, 0.01), mean = 32, sd = 7), 0)
polygon(cord.x, cord.y, col = "blue")
```

###Question 1b: What is the probability of a team scoring more than 35 points? Plot the density function and shade the area:

```{r}
pnorm(35, mean = 32, sd = 7, lower.tail = FALSE)
curve(dnorm(x, mean = 32, sd = 7), from = 11, to = 53)
cord.x <- c(35, seq(35, 53, by = 0.01), 53)
cord.y <- c(0, dnorm(seq(35, 53, 0.01), mean = 32, sd = 7), 0)
polygon(cord.x, cord.y, col = "red")
```

###Question 1c: What is the probability of a team scoring between 20 and 40 points? Plot the density function and shade the area:

```{r}
diff(pnorm(c(20, 40), mean = 32, sd = 7))
curve(dnorm(x, mean = 32, sd = 7), from = 11, to = 53)
cord.x <- c(20, seq(20, 40, by = 0.01), 40)
cord.y <- c(0, dnorm(seq(20, 40, 0.01), mean = 32, sd = 7), 0)
polygon(cord.x, cord.y, col = "green")
```

##Question 2: The number of comment per post on a social media site is exponentially distributed, with the average post recieving ten comments. What percentage of posts get:

###Question 2a: What percentage of posts get fewer than three comments? Plot the density function and shade the area:

```{r}
pexp(3, rate = 1/10)
curve(dexp(x, rate = 1/10), from = 0, to = 40)
cord.x <- c(0, seq(0, 3, by = 0.01), 3)
cord.y <- c(0, dexp(seq(0, 3, 0.01)), 0)
polygon(cord.x, cord.y, col = "blue")  
```

###Question 2b: What percentage of posts has more than 20 comments? Plot the density function and shade the area:

```{r}
pexp(20, rate = 1/10, lower.tail = FALSE)
curve(dexp(x, rate = 1/10), from = 0, to = 40)
cord.x <- c(20, seq(20, 40, by = 0.01), 40)
cord.y <- c(0, dexp(seq(20, 40, 0.01)), 40)
polygon(cord.x, cord.y, col = "red")
```

###Question 2c: What percentage of posts has between five and ten comments? Plot the density function and shade the area:

```{r}
pexp(10, rate = 1/10) - pexp(5, rate = 1/10)
curve(dexp(x, rate = 1/10), from = 0, to = 40)
cord.x <- c(5, seq(5, 10, by = 0.01), 10)
cord.y <- c(0, dexp(seq(5, 10, 0.01)), 0)
polygon(cord.x, cord.y, col = "green")
```

##Question 3: Basic raster creation and calculation:

###Question 3a: Create a first raster (30 rows x 30 columns) and assign values to the raster based on random values from a uniform distribution. Plot the raster and the histogram:

```{r}
library(raster)
set.seed(126)
a <- runif(30)
b <- runif(30)
ras <- raster(nrows = 30, ncols = 30, xmn = 0, xmx = a, ymn = 0, ymx = b)
ras
ras[] <- runif(ncell(ras))
plot(ras)
hist(ras)
```

###Question 3b: Create a second raster (30 rows x 30 columns) and assign values to the raster based on random values from a normal distribution. Plot the raster and the histogram:

```{r}
set.seed(130)
x <- rnorm(30)
y <- rnorm(30)
ras <- raster(nrows = 30, ncols = 30, xmn = 0, xmx = x, ymn = 0, ymx = y)
ras
ras[] <- runif(ncell(ras))
plot(ras)
hist(ras)
```

###Question 3c: Create a third raster (30 rows x 30 columns) and assign values to the raster based on cell-by-cell addition of the first raster and the second raster. Plot the raster and the histogram:

```{r}
c <- a + x
d <- b + y
raster(nrows = 30, ncols = 30, xmn = 0, xmx = c, ymn = 0, ymx = d)
ras
ras[] <- runif(ncell(ras))
plot(ras)
hist(ras)
```

###Question 3d: Calculate the mean value of the third raster. Reclassify the third raster into a binary image: 1 (cell value > mean value) and 0 (cell value <= mean value). Save the reclassified image to your working directory as a TIFF image:

```{r}
cellStats(ras, mean) ##mean of the third raster
ras4 <- reclassify(ras, c(0, 0.4918369, 0,    0.4918369, 1, 1))
ras4
plot(ras4) ##binary image
tiff(filename = "c:\\ras4.tiff", 
     res = 800, pointsize = 2)
plot(ras4)
```

